Figures

### 2020-03-23 manuscript/figures.Rmd
move slope and distance scatter to main figure area

@@

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) buffer slope versus inlake slope.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra=''}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```

>>>>

```{r 01_geometry_grid, fig.cap = "Comparison among lake shape and reservoir classes for A-B) distance to deepest point versus distance to lake visual center and C-D) buffer slope versus inlake slope.", warning=FALSE, echo = FALSE, eval=TRUE, out.extra='', fig.align='center'}
knitr::include_graphics("../figures/01_geometry_grid-1.pdf")
```

@@
